\documentclass[../../../songbook.tex]{subfiles}
\begin{document}
\TabPositions{8cm} %indywidualnie dla piosenki
\section*{YOU'RE BEAUTIFUL}
\phantomsection  
\addcontentsline{toc}{section}{James Blunt - You're Beautiful}
\rightline{(James Blunt-"Back to Bedlam")} 
\rightline{(capo: 3)} 
\vspace{0.5cm}

My life is brilliant. \newline	 

My life is brilliant. My love is pure.	\tab    {\color{red}\textbf{C G} } \newline		
I saw an angel. Of that I'm sure.		\tab    {\color{red}\textbf{a F} } \newline	
She smiled at me on the subway.			\tab    {\color{red}\textbf{C} } \newline	
She was with another man.				\tab    {\color{red}\textbf{G} } \newline	
But I won't lose no sleep on that,		\tab    {\color{red}\textbf{a} } \newline	
'Cause I've got a plan.

\-\hspace{1cm} You're beautiful. You're beautiful.	\tab    {\color{red}\textbf{F G C} } \newline	
\-\hspace{1cm} You're beautiful, it's true.			\tab    {\color{red}\textbf{F G C} } \newline	
\-\hspace{1cm} I saw your face in a crowded place,	\tab    {\color{red}\textbf{F G C/G/a} } \newline	
\-\hspace{1cm} And I don't know what to do,			\tab    {\color{red}\textbf{F G a} } \newline	
\-\hspace{1cm} 'Cause I'll never be with you.		\tab    {\color{red}\textbf{F G C} } \newline	

Yeah, she caught my eye, 							\newline
As we walked on by.									\newline
She could see from my face that I was				\newline
Fucking high 										\newline
And I don't think that I'll see her again,			\newline
But we shared a moment that will last till the end.	\newline

\-\hspace{1cm} You're beautiful...	\newline

You're beautiful. You're beautiful.				\tab    {\color{red}\textbf{F G C} } \newline	
You're beautiful, it's true.					\tab    {\color{red}\textbf{F G C} } \newline	
There must be an angel with a smile on her face,\tab    {\color{red}\textbf{F G C/G/a} } \newline	
When she thought up that I should be with you.	\tab    {\color{red}\textbf{F G C G a} } \newline	
But it's time to face the truth,				\tab    {\color{red}\textbf{F G a} } \newline	
I will never be with you. 						\tab    {\color{red}\textbf{F G C} } \newline	
\end{document}
